### 2025-01-06 skripsi/chapter1.tex
Finish ch4, fix some problems with

Many other fields in physics such as waves, quantum dynamics, fluid dynamics, elastics, and many more also define systems using PDEs. PDEs are also used outside the physical sciences. In Finance, the Black-Scholes-Merton or Black-Scholes equation models the dynamics of the financial market. In ecology, PDEs are used to model population growth which is useful for modelling location dependent carrying capacity. This is used to model species distribution which can help develop better conservation policies. In the social sciences, PDEs such as the cross-diffusion model is used to explore the evolution of the urban environment \autocite{jinDetectingInteractionUrban2023}. Crowd dynamics is another field where researchers have found it useful to model using PDEs \autocite{mukherjeeLagrangianApproachModeling2015,hughesFlowLargeCrowds2000}. These are used to model dynamics such as shock-waves, pathing, and crowd flow as a whole. There are a variety of applications, ranging from bird flocks, pedestrian crowds, to robotic swarms \autocite{gongCrowdDynamicsModeling2023}.

@@

A persistent challenge with all these approaches is the issue of optimization. While neural networks are modular and expressive which is proven by the universal approximation theorem \autocite{cybenkoApproximationSuperpositionsSigmoidal1989,hornikMultilayerFeedforwardNetworks1989}, their loss function present many local minima meaning it is non-convex. This can be mitigated by using advanced optimization techniques that can find a local minima close enough to the global minima such as Adam \autocite{shresthaReviewDeepLearning2019,soydanerComparisonOptimizationAlgorithms2020}. However, the addition of PDE residuals into the loss function have worsened the highly non-convex loss landscape issue \autocite{rathoreChallengesTrainingPINNs2024,NEURIPS2021_df438e52,basirCriticalInvestigationFailure2022}. These problems range from the disparity in size of boundary and residual loss gradients to the fact that incorporation of residuals and boundary conditions themselves create a much more complex loss landscape. As a result, it is desirable to utilize a different machine learning algorithm that possesses a convex loss landscape. One family of such algorithms are Support Vector Machines (SVM) \autocite{vapnikNatureStatisticalLearning2000}. The appeal of SVMs are the fact that the model is formulated as a quadratic programming problem. This means there are strong guarantees for convergence, generalization, and complexity. Another formulation called Least Squares Support Vector Machines (LSSVM) reformulates the problem as a linear system \autocite{suykensLeastSquaresSupport2005}. This leads to an easier problem that can be computed faster by well established algorithms like the many implementations of least squares solvers. Another advantage of the linear formulation is that this can be easily parallelized to exploit hardware like graphics processing units more widely known as GPUs in contrast to the commonly used Sequential Minimal Optimization (SMO) used for SVMs with quadratic objective functions.

@@

\section{Aims}\label{sec:aims}
\noindent Based on the stated problems in \lccref{sec:problem_statement}, this study aims to acomplish the following:
\begin{enumerate}
    \item The design and implementation of a computational model that maps coefficients in the spectral domain using Least Squares Support Vector Regression (LSSVR).
    \item Proof of the model's learning ability using three different problems.
    \item Interpretation the model results and why some predictions turn out the way they do.
\end{enumerate}
% Bagian ini secara tegas menuliskan tujuan pekerjaan penelitian TA, yang dapat memuat lebih dari satu. Pemilihan kata kerja pada Tujuan ini sangat penting karena menggambarkan arah fokus dari jalinan upaya yang dilakukan.

@@

\section{Limitations}
\noindent This work is limited to the following:
\begin{enumerate}
    \item Functions the model works with are only continuous functions.
    \item The basis functions are limited to Fourier basis.
    \item Modeled fields are compact or dense meaning not sparse. Sparse observations or other data are assimilated using other methods.
\end{enumerate}

\section{Sistematika Penulisan}
% \noindent Bagian ini adalah penutup Bab I yang menyampaikan  secara ringkas isi setiap  bab. Karena pembaca sudah sampai akhir Bab I, yang  berarti  sudah  mengetahui isinya, maka tidak perlu ditulis lagi rincian Bab I. Sebaiknya langsung dituliskan secara ringkas isi rincian bab-bab selanjutnya, misalnya, \textit{Setelah Pendahuluan pada Bab I ini, Bab II akan mengulas tentang ...}

>>>>

Many other fields in physics such as waves, quantum dynamics, fluid dynamics, elastics, and many more also define systems using PDEs. PDEs are also used outside the physical sciences. In Finance, the Black-Scholes-Merton or Black-Scholes equation models the dynamics of the financial market. In ecology, PDEs are used to model population growth which is useful for modelling location dependent carrying capacity. This is used to model species distribution which can help develop better conservation policies. In the social sciences, PDEs such as the cross-diffusion model is used to explore the evolution of the urban environment \autocite{jinDetectingInteractionUrban2023}. Crowd dynamics is another field where researchers have found it useful to model using PDEs \autocite{mukherjeeLagrangianApproachModeling2015,hughesFlowLargeCrowds2000}. PDEs have a variety of applications, ranging from bird flocks, pedestrian crowds, to robotic swarms \autocite{gongCrowdDynamicsModeling2023}.

@@

A persistent challenge with all these approaches is the issue of optimization. While neural networks are modular and expressive which is proven by the universal approximation theorem \autocite{cybenkoApproximationSuperpositionsSigmoidal1989,hornikMultilayerFeedforwardNetworks1989}, their loss function present many local minima meaning it is non-convex. This can be mitigated by using advanced optimization techniques that can find a local minima close enough to the global minima such as Adam \autocite{shresthaReviewDeepLearning2019,soydanerComparisonOptimizationAlgorithms2020}. However, the addition of PDE residuals into the loss function have worsened the highly non-convex loss landscape issue \autocite{rathoreChallengesTrainingPINNs2024,NEURIPS2021_df438e52,basirCriticalInvestigationFailure2022}. These problems range from the disparity in size of boundary and residual loss gradients to the fact that incorporation of residuals and boundary conditions themselves create a much more complex loss landscape. As a result, it is desirable to utilize a different machine learning algorithm that possesses a convex loss landscape. One family of such algorithms are Support Vector Machines (SVM) \autocite{vapnikNatureStatisticalLearning2000}. The appeal of SVMs are the fact that the model is formulated as a quadratic programming problem. This means there are strong guarantees for convergence, generalization, and complexity. Another formulation called Least-Squares Support Vector Machines (LSSVM) reformulates the problem as a linear system \autocite{suykensLeastSquaresSupport2005}. This leads to an easier problem that can be computed faster by well established algorithms like the many implementations of least squares solvers. Another advantage of the linear formulation is that this can be easily parallelized to exploit hardware like graphics processing units more widely known as GPUs in contrast to the commonly used Sequential Minimal Optimization (SMO) used for SVMs with quadratic objective functions.

@@

\section{Aims}\label{sec:aims}
\noindent Based on the stated problems in \lccref{sec:problem_statement}, this study aims to accomplish the following:
\begin{enumerate}
    \item The design and implementation of a computational model that maps coefficients in the spectral domain using Least-Squares Support Vector Regression (LSSVR).
    \item Proof of the model's learning ability using three different problems.
    \item Interpretation the model results and why some predictions turn out the way they do.
\end{enumerate}
% Bagian ini secara tegas menuliskan tujuan pekerjaan penelitian TA, yang dapat memuat lebih dari satu. Pemilihan kata kerja pada Tujuan ini sangat penting karena menggambarkan arah fokus dari jalinan upaya yang dilakukan.

@@

\section{Limitations}
\noindent This work is limited to the following:
\begin{enumerate}
    \item Functions the model works with are only continuous functions.
    \item The basis functions are limited to Fourier basis.
    \item Modeled fields are compact or dense meaning not sparse. If this is not true, such as sparse observations, the data would need to be assimilated to create a dense field.
\end{enumerate}

% \section{Sistematika Penulisan}
% \noindent Bagian ini adalah penutup Bab I yang menyampaikan  secara ringkas isi setiap  bab. Karena pembaca sudah sampai akhir Bab I, yang  berarti  sudah  mengetahui isinya, maka tidak perlu ditulis lagi rincian Bab I. Sebaiknya langsung dituliskan secara ringkas isi rincian bab-bab selanjutnya, misalnya, \textit{Setelah Pendahuluan pada Bab I ini, Bab II akan mengulas tentang ...}

### 2025-01-06 skripsi/chapter2.tex
Finish ch4, fix some problems with

Complex numbers are numbers consisting of real and imaginary components. Complex numbers are written as in \lccref{eq:complex_number} with \(a \) and \(b \) being the real and imaginary components respectively. The imaginary component is multiplied by the imaginary unit \(i=\sqrt{-1}\).
\begin{align}
  c = a + bi \label{eq:complex_number} \\
\end{align}
\autocite{DiscreteFourierTransform}
\begin{align}
  c_k=\sum_{n=0}^{N-1} f_n e^{-i2\pi kn/N} \label{eq:discrete_fourier_transform}\\
  f_n=\sum_{k=0}^{N-1} c_k e^{i2\pi kn/N} \label{eq:inverse_discrete_fourier_transform}
\end{align}

@@

Derive the KKT system
\begin{equation}
  \begin{split}
    \pdv{L}{W} = 0 \rightarrow & W = \sum_{k=1}^{n}\alpha_{k}x_{k} \\
    \pdv{L}{b} = 0 \rightarrow & \sum_{k=1}^{n}\alpha_{k} = 0 \\
    \pdv{L}{e_{k}} = 0 \rightarrow & \alpha_{k} = C e_{k} & \qquad k=1,\dots,n\\
    \pdv{L}{\alpha_{k}} = 0 \rightarrow & W^{\intercal}\vb{x}_{k}+b+e_{k} - y_{k} = 0 & \qquad k=1,\dots,n\\
  \end{split}
\end{equation}

@@

In this exmple we will be using the function $2x^2+4$. The values of this function can be seen in Table \ref{table:1}.

>>>>

Complex numbers are numbers consisting of real and imaginary components. Complex numbers are written as in \lccref{eq:complex_number} with \(a \) and \(b \) being the real and imaginary components respectively. The imaginary component is multiplied by the imaginary unit \(i=\sqrt{-1}\).
\begin{align}
  c = a + bi \label{eq:complex_number} \\
\end{align}
\autocite{DiscreteFourierTransform}
\begin{align}
  c_k=\sum_{n=0}^{N-1} f_n e^{-i2\pi kn/N} \label{eq:discrete_fourier_transform} \\
  f_n=\sum_{k=0}^{N-1} c_k e^{i2\pi kn/N} \label{eq:inverse_discrete_fourier_transform}
\end{align}

@@

Derive the KKT system
\begin{equation}
  \begin{split}
    \pdv{L}{W} = 0 \rightarrow          & W = \sum_{k=1}^{n}\alpha_{k}x_{k}                                \\
    \pdv{L}{b} = 0 \rightarrow          & \sum_{k=1}^{n}\alpha_{k} = 0                                     \\
    \pdv{L}{e_{k}} = 0 \rightarrow      & \alpha_{k} = C e_{k}                        & \qquad k=1,\dots,n \\
    \pdv{L}{\alpha_{k}} = 0 \rightarrow & W^{\intercal}\vb{x}_{k}+b+e_{k} - y_{k} = 0 & \qquad k=1,\dots,n \\
  \end{split}
\end{equation}

@@

In this example we will be using the function \(2x^2+4\). The values of this function can be seen in \lccref{table:1}.

### 2025-01-06 skripsi/chapter3.tex
rename files to english versions, add data figures for antiderivative, add content on data and computational model, edit parts of ch 1 & 3
finish ch4 computational model, start implementation
finish second scenario, fix figures and spelling ch4, start third scenario
Finish ch4, fix some problems with

% !TEX root = ./skripsi.tex
\chapter{Research Methodology}\label{sec:research_methodology}

@@

            In this phase, relevant literature of related works and other supporting materials will be reviewed to lay the groundwork of this study. Specifically, the literature review will encompass partial differential equations and their real world associations, traditional methods employed to solve them, systems with partially known or unknown governing equations, machine learning approaches to the problem, least squares support vector machines, performance metrics, and tools that will be used such as the PyTorch library.

@@

            After the computational model design is completed, the model is implemented in the Python Language using the Pytorch library as a core component. Implementation of the computational model is done using an iterative software development model. This development model was chosen due to its adaptability to unexpected challenges which is necessary because of the challenges and unknowns with developing a novel method.

@@

\section{Computational Model Implementation Method}
\noindent Implementation of the computational model follows an iterative development model. This model basically consists of repeated cycles or iterations of software development. Each cycle is loosely based on the waterfall development model, namely the processes of requirement gathering, analysis \& design, implementation, and testing. This iterative property is crucial for this study because all the requirements cannot be known beforehand. This model minimizes the risk in developing complex software with partially known initial requirements. A diagram of the model can be seen in \lccref{fig:iterative_development_diagram}.

@@

\section{Research Tools}
\noindent The tools that are used in this study can be categorized into hardware and software. The following are hardware that are used in this study:
\begin{itemize}
      \item Kaggle CPU Kernel~\autocite{GettingStartedKaggle}
            \begin{itemize}
                  \item 4 Cores Intel Xeon
                  \item 30 Gigabytes RAM
                  \item 20 Gigabytes Working storage
            \end{itemize}
      \item Kaggle GPU Kernel~\autocite{GettingStartedKaggle}
            \begin{itemize}
                  \item 4 Cores Intel Xeon
                  \item 29 Gigabytes RAM
                  \item 1 Nvidia P100 GPU
                  \item 20 Gigabytes Working storage
            \end{itemize}
      \item Personal Computer
            \begin{itemize}
                  \item Intel i5-8300H
                  \item 16 Gigabytes RAM
                  \item Nvidia GeForce GTX 1060 Mobile
                  \item 1.5 Terabytes Storage
            \end{itemize}
\end{itemize}
The software tools used in this study are the following:
\begin{itemize}
      \item Python
      \item Jupyter Notebook
      \item Git
      \item Poetry Python package manager
      \item Web Browser
      \item \LaTeX{}
\end{itemize}

>>>>

% !TEX root = ./skripsi.tex
\chapter{RESEARCH METHODOLOGY}\label{sec:research_methodology}

@@

            In this phase, relevant literature of related works and other supporting materials will be reviewed to lay the groundwork of this study. Specifically, the literature review will encompass partial differential equations and their real world associations, traditional methods employed to solve them, systems with partially known or unknown governing equations, machine learning approaches to the problem, least-squares support vector machines, performance metrics and tools that will be used such as the PyTorch library.

@@

            After the computational model design is completed, the model is implemented in the Python Language using the PyTorch library as a core component. Implementation of the computational model is done using an iterative software development model. This development model was chosen due to its adaptability to unexpected challenges which is necessary because of the challenges and unknowns with developing a novel method.

@@

\section{Computational Model Implementation Method}\label{sec:development_method}
\noindent Implementation of the computational model follows an iterative development model. This model basically consists of repeated cycles or iterations of software development. Each cycle is loosely based on the waterfall development model, namely the processes of requirement gathering, analysis \& design, implementation, and testing. This iterative property is crucial for this study because all the requirements cannot be known beforehand. This model minimizes the risk in developing complex software with partially known initial requirements. A diagram of the model can be seen in \lccref{fig:iterative_development_diagram}.

@@

\section{Research Tools}
\noindent The tools that are used in this study can be categorized into hardware and software. The following are hardware that are used in this study:
\begin{itemize}
      \item Kaggle CPU Kernel~\autocite{GettingStartedKaggle}
            \begin{itemize}
                  \item 4 Cores Intel Xeon
                  \item 30 Gigabytes RAM
                  \item 20 Gigabytes Working storage
            \end{itemize}
      \item Kaggle GPU Kernel~\autocite{GettingStartedKaggle}
            \begin{itemize}
                  \item 4 Cores Intel Xeon
                  \item 29 Gigabytes RAM
                  \item 1 Nvidia P100 GPU
                  \item 20 Gigabytes Working storage
            \end{itemize}
      \item Personal Computer
            \begin{itemize}
                  \item Intel i5{-}8300H
                  \item 16 Gigabytes RAM
                  \item Nvidia GeForce GTX 1060 Mobile
                  \item 1.5 Terabytes Storage
            \end{itemize}
\end{itemize}
The software tools used in this study are the following:
\begin{itemize}
      \item Python
      \item Jupyter Notebook
      \item Git
      \item Poetry Python package manager
      \item Web Browser
      \item \LaTeX{}
\end{itemize}
